Manuscript

### 2016-03-06 inst/simulation/manuscript.Rmd
...

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(STREM)
source("~/git/STREM/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)

@@

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        #plot.margin=unit(c(0, 0.1, 0, 0), units="line"), #top, right, bottom, and left margins
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_colour_manual("CI", values=c("black", "grey")) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          panel.margin=unit(0, units="line"),
          #legend.margin=unit(-1, units="line"),
          #legend.position="bottom",
          legend.direction="vertical",
          #legend.direction="horizontal",
          legend.box="horizontal",
          legend.key.height=unit(0.7, "line"))
          #legend.key.width=unit(.7, "line"),
          #legend.key.height=unit(0, "line"))

>>>>

```{r initialize}
#library(devtools); install_github("statguy/STREM")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(STREM)
source("~/git/STREM/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)

@@

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CrI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CrI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_colour_manual("CrI", values=c("black", "grey"), guide=guide_legend(override.aes=list(size=3.5, shape=15))) +
    theme_ms() +
    theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          panel.margin=unit(0, units="line"),
          legend.direction="vertical",
          legend.box="horizontal",
          legend.key.height=unit(0.7, "line"))
    #guides(scale_colour_manual=guide_colourbar())
